Stochastic Variance Reduced Policy Gradient

### 2018-02-01 svrpg.tex
correzioni sulla sezione  practical variants

As reported in Section \ref{subsec:PolicyGradient} in practical variants we use G(PO)MDP gradient estimator~\cite{baxter2001infinite}, that brings the same guarantees of Reinforce Estimator.
One variant in off-policy G(PO)MDP is to use the weighted per-decision importance sampling estimator \cite{precup2000eligibility}:  this allows a reduction of the gradient estimator variance. The off-policy gradient estimator becomes:
\begin{align*}
\gradApp{\vtheta}{N} = \frac{1}{\Omega}\sum_{n=1}^{N}\sum_{h=0}^{H-1}\left(\sum_{k=0}^{h}\score{\vtheta}{a_k^n\mid s_k^n}\right)\left(\gamma^h r_h^n \omega(z_{0:h})\right).
\end{align*} 
where:
\begin{align*}
\omega(z_{0:h}) = \prod_{k=0}^{h} \frac{\pi_{\vtheta}({a_k^n\mid s_k^n})
 }{\pi_{\vtheta^{'}}({a_k^n\mid s_k^n})}
\end{align*}
\begin{align*}
\Omega = \sum_{n=1}^{N}\sum_{h=0}^{H-1}\gamma^h\prod_{k=0}^{h} \frac{\pi_{\vtheta}({a_k^n\mid s_k^n})
}{\pi_{\vtheta^{'}}({a_k^n\mid s_k^n})}
\end{align*}

>>>>

As reported in Section \ref{subsec:PolicyGradient} we use G(PO)MDP gradient estimator~\cite{baxter2001infinite}, which gives us the same guarantees we have for the Reinforce Estimator.
One variant in off-policy G(PO)MDP is to use the weighted per-decision importance sampling estimator \cite{precup2000eligibility}, allowing a reduction of the gradient estimator variance. The off-policy gradient estimator becomes:
\begin{align*}
\gradApp{\vtheta}{N} = \frac{1}{\Omega}\sum_{n=1}^{N}\sum_{h=0}^{H-1}\left(\sum_{k=0}^{h}\score{\vtheta}{a_k^n\mid s_k^n}\right)\left(\gamma^h r_h^n \omega(z_{0:h})\right).
\end{align*} 
where:
\begin{align*}
\omega(z_{0:h}) = \prod_{k=0}^{h} \frac{\pi_{\vtheta}({a_k^n\mid s_k^n})
 }{\pi_{\vtheta^{'}}({a_k^n\mid s_k^n})}
\end{align*}
\begin{align*}
\Omega = \sum_{n=1}^{N}\sum_{h=0}^{H-1}\gamma^h\prod_{k=0}^{h} \frac{\pi_{\vtheta}({a_k^n\mid s_k^n})
}{\pi_{\vtheta^{'}}({a_k^n\mid s_k^n})}
\end{align*}
